SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-13 docs/questioning.tex
a reference from Software Engineering correlating testing with better design
editing conclusions

While describing the various mechanisms in Section~\ref{sec:defs}, we
observed that some can be bypassed by attackers that know how they
work. Still, some mechanisms are designed in such a way so that they
can be extended and become immune to the attacks that they are
currently vulnerable to. For example, policy enforcement frameworks
that are based on JavaScript or {\sc html} rewriting can be extended
to detect attacks that leverage {\tt iframe} tags. This does not apply
to all mechanisms though. In particular, training mechanisms like {\sc
  didafit} and {\sc xss-guard} must be redesigned to detect the
attacks we described in the related sections.

An interesting observation is that mimicry attacks can be
used to bypass mechanisms coming from the hybrid category and
the policy enforcement and training subcategories.

@@

We need to mention that the fact that mechanisms come sometimes with
deployment difficulties does not necessarily mean that this is a
serious reason not to adopt them. The deployment of such frameworks is
most of the time complex because as we observed in
Section~\ref{sec:attacks} the attacks that they detect are complex
too. So every security feature can come with such a trade-off and
those who intend to use it should be aware of this.

Deployment can also depend on the detection point of an attack. We saw
that many policy enforcement mechanisms that detect attacks at Point
{\sc ub}, are not easy to deploy because modifications are needed both
on the server and the client side. We observed though that Blueprint
has not such deployment issues (see Subsection~\ref{sec:deploy2}).
Thus, when developing a new countermeasure, researchers should
consider where they are planning to detect attacks, observe the
corresponding deployment challenges, and try to mitigate them.

@@

In our research we tried to identify some of the reasons
why this is the case. Some of these reasons include
poor testing, high overhead, code unavailability,
deployment and security issues. However, our
systematization suggests that there are many
promising cases. For instance there are
mechanisms that have been extensively
tested in terms of accuracy ({\sc sqlc}heck, {\sc amnesia},
{\sc dsi}, libAnomaly), solve specific
problems in an efficient way (Blueprint and the system
by Stock et al.) or have a low computational overhead
({\sc dsi} and the system by Phung et al.).
There are also cases where researchers have made their
code available ({\sc beep} and {\sc sd}river) which
can be a push towards the development of better
mechanisms. This argument has been raised
by another {\sc s}o{\sc k} paper too~\cite{SPWS13}.
Finally, we believe that testing defenses in
a production setting could also propel their adoption.

We hope that the exploitation model, analysis
and observations that emerged from our research
can be a reference point for researcher who
wish to develop new countermeasures that
detect web application attacks.

>>>>

While describing the various mechanisms in Section~\ref{sec:defs}, we
observed that some can be bypassed by attackers that know how they
work. Still, some mechanisms are designed in such a way that they
can be extended and become immune to the attacks that they are
currently vulnerable to. For example, policy enforcement frameworks
that are based on JavaScript or {\sc html} rewriting can be extended
to detect attacks that leverage {\tt iframe} tags. This does not apply
to all mechanisms though. In particular, training mechanisms like {\sc
  didafit} and {\sc xss-guard} must be redesigned to detect the
attacks we described in the related sections.

Taking the attackers' point of view, mimicry attacks can affect a
range of different mechanisms: they can be used to bypass mechanisms
in the hybrid category, as well as the policy enforcement and training
subcategories.

@@

The deployment difficulties we have found with many mechanisms are not
a reason not to adopt them, but they may hinder their widespread use.
Since source code injection attacks are complex, it may be logical to
expect that mechanisms to detect them would be complex too. The effort
to install and use a tool should be weighed against the expected
benefits. That is one more reason why it is important to report tool
accuracy, as this provides an immediate indicator to the expected
benefits.

The issue is more acute when the point of detection is at the client.
We saw that many policy enforcement mechanisms that detect attacks at
Point {\sc ub} are not easy to deploy because modifications are needed
both on the server and the client side. It is unrealistic to expect
the average web user to go through complicated installation and
configuration procedures. Conversely, it may be possible to deliver
the tools to the user unobtrusively; for example, we saw that
Blueprint enforces policies on the client side by embedding a library
in the server's response to the client. In general, when developing a
new countermeasure, researchers should consider where they are
planning to detect attacks, observe the corresponding deployment
challenges, and try to mitigate them.

@@

In order for a security tool to be used in practice it must provide
some value to the user. In particular, the value should outweigh the
cost of its use. The cost need not be directly monetary, but may be
incurred from the time required to use the tool, any inconvenience
caused, false alarms that it may raise. These costs are related to the
issues we have been investigating here: poor testing, high overhead,
unavailabilty of source, deployment difficulties, security issues.

Enhancing any of these would not just increase the value of a piece of
research as a practical tool, it would increase its research value as
well. Accurate detection reporting would help in appraising different
approaches. Performance measurements can point to blind, unpractical,
alleys and focus effort elsewhere. Availability of source code
enhances basic scientific tasks like checking and replication. Ease of
deployment brings ease of experimentation. Secure methods can form the
basis for developing methods with more extensive coverage.

We saw that there are mechanisms that have been extensively tested in
terms of accuracy ({\sc sqlc}heck, {\sc amnesia}, {\sc dsi},
libAnomaly), solve specific problems in an efficient way (Blueprint
and the system by Stock et al.) or have a low computational overhead
({\sc dsi} and the system by Phung et al.). There are also cases where
researchers have made their code available ({\sc beep} and {\sc
  sd}river) which can be a push towards the development of better
mechanisms. This argument has been raised by another {\sc s}o{\sc k}
paper~\cite{SPWS13}. Furthermore, testing defenses in a production
setting could also propel their adoption.

We hope that the exploitation model, analysis, and observations that
emerged from our research can be a reference point for researchers who
wish to develop new countermeasures against web application
attacks.
